### 2015-11-25 ch02-qlogms/excitation-design.tex
Figure aperiodic removed from text
And some structure work on CH02

  \begin{example}
   Consider the generalized multisine of the previous example to which a spectral component is added at $f_3 = \pi \unit{Hz}$, or equivalently one with a period of $T_3 = \pi^{-1} \unit{s}$.
   Then it is not possible to determine integer values $n_1$, $n_2$, $n_3$ such that $n_1 T_1 = n_2 T_2 = n_3 T_3$.
   Consequently, such a `multisine' is not periodic.
  \end{example}

@@

  \begin{remark}
    In different contexts, e.g. electrical circuit simulators such as \gls{SPICE}~\citep{Kundert1995}, measurement equipment such as \glspl{DSA} or the \code{logspace} function in \MATLAB it is more common to specify the spacing of a logarithmic grid using the total number of frequencies ($F$) or the number of frequencies per decade ($F_{\decade}$).
  \end{remark}

  \begin{property}
   Each frequency band $B = \ClosedInterval{f, \kappa f}$ with $\kappa \in \PositiveRealNumbers \without \set{0,1}$ that is completely within the range of the excited logarithmic grid of frequencies $\set{f_1, \ldots, f_F}$ contains a constant number of frequency lines
   \begin{equation}
     F_{B} \isdef
     \floor{\frac{\log (\kappa f) - \log( f )}{\log \alpha}}
         = \floor{\log_{\alpha} \kappa}
         \text{.}
   \end{equation}
   \end{property}
  \begin{example}
    For the frequency decade band $\decade(f) \isdef \ClosedInterval{f, 10 f}$, a logarithmic frequency grid contains $F_{\decade} = \floor{\log_{\alpha} 10}$ excited lines.
  \end{example}
  \begin{example}
    The~\citep{HP3562A} has a logarithmic measurement mode that ensures that each decade is covered by $F_{\decade} = 80$ lines~ to measure an \gls{FRF}.
    This is equivalent to a grid spacing $\alpha = \sqrt[80]{10} \approx 1.029$.
  \end{example}

>>>>

  \begin{example}
   Consider the generalized multisine of the previous example to which a spectral component is added at $f_3 = \pi \unit{Hz}$, or equivalently one with a period of $T_3 = \pi^{-1} \unit{s}$.
   Then it is not possible to determine integer values $n_1$, $n_2$, $n_3$ such that $n_1 T_1 = n_2 T_2 = n_3 T_3$ since $T_3$ is an irrational number (unlike $T_1$ and $T_2$).
   Consequently, such a generalized `multisine' is not periodic.
  \end{example}

@@

  \begin{property}
   Each frequency band $B = \ClosedInterval{f, \kappa f}$ with $\kappa \in \PositiveRealNumbers \without \set{0,1}$ that is completely within the range of the excited logarithmic grid of frequencies $\set{f_1, \ldots, f_F}$ contains a constant number of frequency lines
   \begin{equation}
     F_{B} \isdef
     \floor{\frac{\log (\kappa f) - \log( f )}{\log \alpha}}
         = \floor{\log_{\alpha} \kappa}
         \text{.}
   \end{equation}
   \end{property}
  \begin{example}
    For the frequency decade band $\decade(f) \isdef \ClosedInterval{f, 10 f}$, a logarithmic frequency grid contains $F_{\decade} = \floor{\log_{\alpha} 10}$ excited lines.
  \end{example}
  \begin{remark}
    In different contexts, e.g. electrical circuit simulators such as \gls{SPICE}~\citep{Kundert1995}, measurement equipment such as \glspl{DSA} or the \code{logspace} function in \MATLAB it is more common to specify the spacing of a logarithmic grid using the total number of frequencies ($F$) or the number of frequencies per decade ($F_{\decade}$).
    Obviously, such alternative specifications are equivalent.
  \end{remark}
  \begin{example}
    The~\citep{HP3562A} has a logarithmic measurement mode that ensures that each decade is covered by $F_{\decade} = 80$ lines~ to measure an \gls{FRF}.
    This is equivalent to a grid spacing $\alpha = \sqrt[80]{10} \approx 1.029$.
  \end{example}
